Topic modeling on EU and the USA research projects

### 2017-06-21 thesis_report/draft_thesis.tex
Appendix wordclouds (5/10)

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic0_7000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic1_7000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic2_7000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic3_7000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic4_7000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic5_7000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic6_7000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic7_7000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic8_7000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic9_7000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU FP6 (2002-2006)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic0_7000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic1_7000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic2_7000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic3_7000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic4_7000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic5_7000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic6_7000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic7_7000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic8_7000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic9_7000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU FP7 (2007-2013)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic0_20000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic1_20000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic2_20000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic3_20000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic4_20000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic5_20000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic6_20000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic7_20000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic8_20000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic9_20000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU H2020 (2014-2020)}
\end{figure}
\end{center}

>>>>

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[International research]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic0_7000.png}} &
\subfloat[Biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic1_7000.png}}&
\subfloat[Embedded systems design]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic2_7000.png}}\\
\subfloat[Molecular biology, genes]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic3_7000.png}}&
\subfloat[Evolution / Formation]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic4_7000.png}} &
\subfloat[Sustainable production / Energy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic5_7000.png}}\\
\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic6_7000.png}} &
\subfloat[Environmental management services]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic7_7000.png}}&
\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic8_7000.png}}\\
\subfloat[Cognitive neuroscience]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic9_7000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU FP6 (2002-2006)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Cancer detection \& treatment]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic0_7000.png}} &
\subfloat[(High energy) physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic1_7000.png}}&
\subfloat[Energy production]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic2_7000.png}}\\
\subfloat[Social Sciences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic3_7000.png}}&
\subfloat[Molecular Biology / Genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic4_7000.png}} &
\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic5_7000.png}}\\
\subfloat[International research]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic6_7000.png}} &
\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic7_7000.png}}&
\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic8_7000.png}}\\
\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic9_7000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU FP7 (2007-2013)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic0_20000.png}} &
\subfloat[Environmental sustainability \& food production]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic1_20000.png}}&
\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic2_20000.png}}\\
\subfloat[?]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic3_20000.png}}&
\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic4_20000.png}} &
\subfloat[Environmental sustainability / Green energy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic5_20000.png}}\\
\subfloat[Physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic6_20000.png}} &
\subfloat[Business \& Innovation]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic7_20000.png}}&
\subfloat[Cancer detection \& treatment]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic8_20000.png}}\\
\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic9_20000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU H2020 (2014-2020)}
\end{figure}
\end{center}
